BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2014-10-14 Paper/BOAST.tex
improved bibliography

  Collective Mind

  Adaptive Sampling Kit (ASK)

>>>>

  Once auto-tuning technique are used the parameter space explodes and the
systematic sampling rapidly becomes impossible to achieve. The cost of finding
the optimal kernel parameters and environment parameters (compiler flags, used
language, ...) is rapidly prohibitive. Dedicated frameworks have been developed
to address this problem. Adaptive Sampling Kit (ASK)~\cite{castro2013adaptive}
is one such tool. It reduces the number of sample needed by creating a model of
the performances and by minimizing the number of samples needed to find the
parameters of this model. Several models and sampling techniques are
implemented.

  Collective Mind~\cite{fursin:hal-01054763} proposes similar techniques to
solve the problem but also stores and the results and complete experimental
setups in databases for future reference and reproducibility. This database
approach also enables easy parallelization of the experimental process.
Collective Mind also proposes collections of flags for many available
compilers/versions easing the exploration process.
